---
title: "W_UP_01"
author: "Marta Marriott"
date: "Spring 2024"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Plot boxplots

```{r}
boxplot(pushups~position,data=mydata)
```

The boxplot shows the average number of pushups between line and skill players , the boxplot represents the data that was collected. The average number of pushups was higher for skill players compared to  line players. The median among line players was 17, with the median among skill players was roughly 50.
    
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```
When comparing the data analysis from the boxplot line and skill players, the median for both and additional data such as the highest averages of pushups for each group in the boxplot, which are represented in Q1 and Q3. They show the  statistical differences when the data is being comapred.
  
## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```
The data collected is 0.000009421 concludes the difference is quite large and the difference shows betweent eh two groups where the data was collected line and skill there is a 95% difference because they are both statistically different from one another.
  
# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The required tools were used in order to show the statistical differences in pushups. First, we used a boxplot for a visual representation of the data. Secondly, a numerical description was used in order to numerically convey they statistical differences by comparing the data being shown in thee boxplot. And finally, we ran a t-test to show how statistically different the two data points actually were to understand they had a 95% difference from one another and thus was the reason for the different data points in the boxplot and numerical data.